---
title: "The bioAnno package"
author:
- name: Kai Guo
  affiliation:
  - Biomedical Sciences, University of North Dakota
date: "`r Sys.Date()`"
output:
  html_document:
  df_print: paged
  word_document:
    toc: yes
    toc_depth: '6'
  rmarkdown::html_vignette: default
  pdf_document:
    toc: yes
    toc_depth: 6
vignette: |
  \usepackage[utf8]{inputenc}
  %\VignetteIndexEntry{bioAnno}
  %\VignetteEngine{knitr::knitr}
---
__bioAnno__ An R package for building annotation package by using
information from __KEGG__, __NCBI__, __Ensembl__ and return OrgDb object
such as org.Hs.eg.db.   

## 1. Introduction

With the increasing of high throughput data generated, the requirement for
having annotation package ready is necessary for people doing functional 
enrichment analysis, id conversion and other type related analysis.
_bioAnno_ provide wrap functions include _fromKEGG_, _fromEnsembl_, 
_fromNCBI_ and _fromAnnoHub_ to build annotation package. 
And you can easily to build annotation package with 
the KEGG species code (except _fromEnsembl_ which require scientific name).

## 2. Software Usage
### 2.1 Installation
The package can be installed as (preparing to submit to bioconductor)
``` {r install, eval = FALSE}
if (!requireNamespace("BiocManager"))
    install.packages("BiocManager")
BiocManager::install("VennDetail")
```
### 2.2 Load package
```{r load, results = 'hide', message = FALSE}
library(bioAnno)

```

### 2.3 Quick Tour
``` {r quick}
library(bioAnno)
## build Annotation package by using fromKEGG
fromKEGG(species="ath")
## which will build and install package "org.hsa.eg.db" which will include
## KEGG, GO annotation build from AnnotationHub
fromAnnHub(species="ath")
```
### 2.4 Main Functions
--  _fromKEGG_ build annotation package by extracting annotation information 
    from Kyoto Encyclopedia of Genes and Genomes database (KEGG). 
    You can use KEGG species code as query species name.

-- _fromNCBI_ build annotation package by extracting annotation information from
    NCBI database.

-- _fromENSEMBL_ build annotation package by extracting annotation information 
    fromENSEMBL database. It includes function to build annotaion package for 
    plant with parameter plant = TRUE
-- _fromAnnhub_ build annotation package with the AnnotationHub package 

## 3 Contact information

For any questions please contact guokai8@gmail.com

