---
title: "The bioAnno package"
author:
- name: Kai Guo
  affiliation:
  - Biomedical Sciences, University of North Dakota
date: "`r Sys.Date()`"
output:
  html_document:
  df_print: paged
  word_document:
    toc: yes
    toc_depth: '6'
  rmarkdown::html_vignette: default
  pdf_document:
    toc: yes
    toc_depth: 6
vignette: |
  \usepackage[utf8]{inputenc}
  %\VignetteIndexEntry{bioAnno}
  %\VignetteEngine{knitr::knitr}
---
__bioAnno__ An R package for building annotation package by using
information from __KEGG__, __NCBI__, __Ensembl__ and return OrgDb object
such as org.Hs.eg.db.
## 1. Introduction

_bioAnno_ provide wrap functions _fromKEGG_, _fromEnsembl_,_fromNCBI_ and _fromAnnoHub_ to
build annotation package. KEGG species code is suggested to use except _fromEnsembl_
which require scientific name.

## 2. Software Usage
### 2.1 Installation
The package can be installed as (preparing to submit to bioconductor)
``` {r install,eval = FALSE}
library(devtools)
install_github("guokai8/bioAnno")
```
### 2.2 Load package
```{r load, results = 'hide', message = FALSE}
library(bioAnno)

```

### 2.3 Quick Tour
``` {r quick, eval = FALSE}
library(bioAnno)
## build Annotation package by using fromKEGG
fromKEGG(species="hsa")
## which will build and install package "org.hsa.eg.db" which will include
## KEGG, GO annotation
## build from AnnotationHub
fromAnnHub(species="human")
```
## Note
The _bioAnno_  provide wrap function which help me to
easily build annotation package.

## 3 Contact information

For any questions please contact guokai8@gmail.com

