---
title: "The bioAnno package"
author:
- name: Kai Guo
  affiliation:
  - Biomedical Sciences, University of North Dakota
date: "`r Sys.Date()`"
output:
  html_document:
  df_print: paged
  word_document:
    toc: yes
    toc_depth: '6'
  rmarkdown::html_vignette: default
  pdf_document:
    toc: yes
    toc_depth: 6
vignette: |
  \usepackage[utf8]{inputenc}
  %\VignetteIndexEntry{bioAnno}
  %\VignetteEngine{knitr::knitr}
---
__bioAnno__ An R package for building annotation package by using
information from __KEGG__, __NCBI__, __Ensembl__ and return OrgDb object
such as org.Hs.eg.db.   

## 1. Introduction

With the increasing of high throughput data generated, the requirement for
having annotation package is necessary for people who want to do functional 
enrichment analysis, id conversion and other type related analysis.
_bioAnno_ provide wrap functions include _fromKEGG_, _fromEnsembl_, 
_fromNCBI_ and _fromAnnoHub_ to build annotation package. 


## 2. Software Usage
### 2.1 Installation
The package can be installed with following command 
``` {r install, eval = FALSE}
if (!requireNamespace("BiocManager"))
    install.packages("BiocManager")
BiocManager::install("bioAnno")
```
### 2.2 Load package 
```{r load, results = 'hide', message = FALSE}
library(bioAnno)

```

### 2.3 Quick Tour
``` {r quick}
library(bioAnno)
## build arabidopsis thaliana annotation package by using fromKEGG function from
## KEGG database.
fromKEGG(species="ath", install = FALSE)
## which will build "org.ath.eg.db" package. The package contains
## KEGG, GO annotation. You can use install = TRUE to direct 
## install the package. 
## build from arabidopsis thaliana annotation package by using fromAnnHub 
## function
fromAnnHub(species="ath", install = FALSE)
```
### 2.4 Main Functions
--  _fromKEGG_ build annotation package by extracting annotation information 
    from Kyoto Encyclopedia of Genes and Genomes (KEGG) database. 
    You can use KEGG species code as the query name.

-- _fromNCBI_ build annotation package by extracting annotation information from
    NCBI database.

-- _fromENSEMBL_ build annotation package by extracting annotation information 
    fromENSEMBL database. It includes function to build annotaion package for 
    plant with parameter plant = TRUE.  
    
-- _fromAnnhub_ build annotation package with the AnnotationHub package 

-- _getTable_ get annotataion table from temporary package

## 3 Contact information

For any questions please contact guokai8@gmail.com

