---
title: "The bioAnno package"
author:
- name: Kai Guo
  affiliation:
  - Biomedical Sciences, University of North Dakota
date: "`r Sys.Date()`"
output:
  html_document:
  df_print: paged
  word_document:
    toc: yes
    toc_depth: '6'
  rmarkdown::html_vignette: default
  pdf_document:
    toc: yes
    toc_depth: 6
vignette: |
  \usepackage[utf8]{inputenc}
  %\VignetteIndexEntry{bioAnno}
  %\VignetteEngine{knitr::knitr}
---
__bioAnno__ An R package for building annotation package by using
information from __KEGG__, __NCBI__, __Ensembl__ and return OrgDb object
such as org.Hs.eg.db.   

## 1. Introduction

With the increasing of high throughput data generated, the requirement for
having annotation package is necessary for people who want to do functional 
enrichment analysis, id conversion and other type related analysis.
_bioAnno_ provides wrap functions include _fromKEGG_, _fromEnsembl_, 
_fromNCBI_ and _fromAnnoHub_ to build annotation package. Making Organism 
Packages is a straightforward process using the helper functions _fromKEGG_, 
_fromNCBI_ and from fromAnnoHub. Moreover, users are also allowed to make their
own package based on their own annotation file by using _fromOwn_.


## 2. Software Usage
### 2.1 Installation
The package can be installed with following command 
``` {r install, eval = FALSE}
if (!requireNamespace("BiocManager"))
    install.packages("BiocManager")
BiocManager::install("bioAnno")
```
### 2.2 Load package 
```{r library, results = 'hide', message = FALSE}
library(bioAnno)

```

### 2.3 How to use it
``` {r quick, message=FALSE}
library(bioAnno)
## build E.coli annotation package by using fromKEGG function from
## KEGG database.
fromKEGG(species="eco", install = FALSE)
## which will build "org.eco.eg.db" package. The package contains
## KEGG, GO annotation. You can use install = TRUE to direct 
## install the package. 
## build from arabidopsis thaliana annotation package by using fromAnnHub 
## function
fromAnnHub(species="ath", install = FALSE)
```
### 2.4 Main Functions
--  _fromKEGG_ build annotation package by extracting annotation information 
    from Kyoto Encyclopedia of Genes and Genomes (KEGG) database. 
    You can use KEGG species code as the query name.

-- _fromNCBI_ build annotation package by extracting annotation information from
    NCBI database.

-- _fromENSEMBL_ build annotation package by extracting annotation information 
    fromENSEMBL database. It includes function to build annotaion package for 
    plant with parameter plant = TRUE.  
    
-- _fromAnnhub_ build annotation package with the AnnotationHub package 

-- _getTable_ get annotataion table from temporary package which need user provide the temporary path

## 3 To use the annotation package user created
An organism level package (an ‘org’ package) you created uses a central gene 
identifier and contains mappings between this identifier and other kinds of
identifiers. The most common interface for retrieving data is the _select_
method.
```{r load, message = FALSE}
#First make your own anntation package and loading the package
data(ath)
fromOwn(geneinfo = ath, install = TRUE)
library(org.species.eg.db)
```
There are 4 common methods that work together to allow a select interface. The
1st one is _columns_, which help you to discover which sorts of annotations can be extracted
from it.
```{r columns, message = FALSE }
columns(org.species.eg.db)
```
The next method is _keytypes_ which tells you the kinds of things that can be used as
keys.
```{r keytypes, message = FALSE }
keytypes(org.species.eg.db)
```
The third method is _keys_ which is used to retrieve all the viable keys of a particular
type.
```{r keys, message = FALSE}
key <- keys(org.species.eg.db,keytype="ENTREZID")
```
And finally there is _select_, which extracts data by using values supplied by the other method
```{r select, messgae = FALSE}
result <- select(org.species.eg.db, keys=key,
columns=c("GID","GO","PATH"),keytype="ENTREZID")
head(result)
```
Users are also allowed to use mapIds extract gene identifiers
KEGG pathway from the annotation package.
```{r mapIds, message = FALSE}
KEGG<-mapIds(org.species.eg.db,keys=key,column="PATH",keytype="ENTREZID")
head(KEGG)
```
Or for id conversion
```{r id, message = FALSE}
mapIds(org.species.eg.db,keys=key[1:10],column="GID",keytype="ENTREZID")
```
The version number of R and packages loaded for generating the vignette were:
```{r version, message = FALSE}
sessionInfo()
```



